### 2014-12-09 ThesisJo/derivations.tex
la2pdf commit - 2014:11:26	19:44:01	(on.26.nov.)
More derivations
la2pdf commit - 2014:12:09	10:55:51	(Tue 9.Dec)

Various adaptive beamformers target this limitation by allowing the weights to change for each pixel to better fit the dynamic nature of the incoming wavefield. In other words, they attempt to use the \emph{a priori} information present in the data to improve image quality. The MVDR beamformer is one such method. It finds the set of complex weights that minimizes the beamformer's expected output power, while ensuring unity gain in the look direction~\cite{Capon1969}. This is a convex optimization problem that can be solved using Lagrange multipliers to yield the solution
\begin{gather}
\vec w[n] = \frac{\Ri[n]\a}{\a\T\Ri[n]\a},\label{weights}
\end{gather}
where $\a$ is a steering vector and $\R=E\{\x[n]\x\H[n]\}\in\mathbb{C}^{M,M}$ is the spatial covariance matrix for the full array. Since we pre-steer our data to every pixel in the image we simplify (\ref{weights}) by substituting $\a$ with a row vector $\1$ that represents broadside phase-steering. To estimate $\R$ we compute a sample covariance matrix $\eR$. In this computation we perform some degree of:
\begin{itemize}
\item \emph{spatial averaging} to avoid signal cancellation by decorrelating coherent echoes~\cite{Kailath1985};
\item \emph{temporal averaging} over an interval comparable to the pulse length (one to five samples) to maintain true speckle statistics~\cite{Synnevag2009a};
\item \emph{diagonal loading} to improve robustness to parameter errors~\cite{Cox1987,Maksym1979}.
\end{itemize}%

>>>>

Various adaptive beamformers target this limitation by allowing the weights to change for each pixel to better fit the dynamic nature of the incoming wavefield. In other words, they attempt to use the \emph{a priori} information present in the data to improve image quality. The MVDR beamformer is one such method. It finds the set of complex weights that minimizes the beamformer's expected output power, while ensuring unity gain in the look direction~\cite{Capon1969}. This is a convex optimization problem that can be solved using Lagrange multipliers to yield the solution
%
\begin{gather}
\vec w[n] = \frac{\Ri[n]\a}{\a\T\Ri[n]\a},\label{weights}
\end{gather}
%
where $\a$ is a steering vector and $\R=E\{\x[n]\x\H[n]\}\in\mathbb{C}^{M,M}$ is the spatial covariance matrix for the full array. Since we pre-steer our data to every pixel in the image we simplify (\ref{weights}) by substituting $\a$ with a row vector $\1$ that represents broadside phase-steering. To estimate $\R$ we compute a sample covariance matrix $\eR$. In this computation we perform some degree of:
%
\begin{itemize}
\item \emph{spatial averaging} to avoid signal cancellation by decorrelating coherent echoes~\cite{Kailath1985};
\item \emph{temporal averaging} over an interval comparable to the pulse length (one to five samples) to maintain true speckle statistics~\cite{Synnevag2009a};
\item \emph{diagonal loading} to improve robustness to parameter errors~\cite{Cox1987,Maksym1979}.
\end{itemize}%

\subsection{Diagonal loading}

Assume the data to be a combination of signal and noise, $\x = \s + \n = e^{j\theta[n]}$. Then the beamformer output is
%
\begin{align}
z = \w\H\x = \w\H(\s+\n),
\end{align}
%
and the output power becomes
%
\begin{align}
|z|^2 = \w\H\x\x\H\w &= \w\H(\s+\n)(\s+\n)\H\w \nn
&= \begin{cases}
\w\H\s\s\H\w + \w\H\s\n\H\w + \w\H\n\s\H\w + \w\H\n\n\H\w &\text{when correlated}\\
\w\H\s\s\H\w + \w\H\n\n\H\w &\text{when uncorrelated}
\end{cases}
\end{align}
%
Assuming that the data is predelayed broadside, and that the window is rectangular, we may set $\a = \s$ and get
%
\begin{align}
|z|^2 = \w\H\s\s\H\w + \w\H\n\n\H\w
\end{align}

\section{Beamforming}

\begin{align}
z[n] = \w\H[n]\x[n]
\end{align}
